\chapter{EXPECTED RESULTS}

The implementation of a social media platform for the people of science is anticipated to yield the following outcomes. These expected results are aligned with the project objectives and will contribute to the establishment of a space for scientific communicators in the wider network of the Fediverse:

\begin{enumerate}
    \item \textbf{Foster Scientific Community:} 
    \begin{itemize}
        \item With the ability to use scientific typesetting, users will be able to express their thoughts better than in regular plain text.
        \item Connecting the scientific instance with the Fediverse will help more people become aware of the presence of the scientific community. The more people post, the more others will know.
    \end{itemize}

    \item \textbf{Increased User Control:} 
    \begin{itemize}
        \item Users will have full ownership of their data if they decide to host the platform themselves.
        \item Users will have increased privacy since the data will not be under a big tech corporation but rather individually controlled servers. 
    \end{itemize}

    \item \textbf{Better Engagement:} 
    \begin{itemize}
        \item Users will be connected to the wider network of the Fediverse, eliminating the need for wide adoption to enable user interaction.
        \item With how the Fediverse works, users can choose to interact with the people they want to be around (e.g., only within the scientific community) or with the wider general audience.
    \end{itemize}
\end{enumerate}
